---
title: "Combined"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

* Read csv file
```{r}
veh = read.csv("../URAP2/2017 NHTS/vehpub.csv")
hh = read.csv("../URAP2/2017 NHTS/hhpub.csv")
```

* Aggregate bestmile 
```{r}
for(i in 1:nrow(hh)){
  hh$BESTMILE[i]=sum(veh[veh$HOUSEID==hh[i,1],"BESTMILE"])
} ##we put "BESTMILE" in "hh"
write.csv(hh,"recs.csv")
```

* National Household Travel Survey

We will created new dummy variables for races. When we use a regression model, we have to choose the baseline dummy to prevent "Multicollinearity". 

Supporting info: https://analyticstraining.com/understanding-dummy-variable-traps-regression/


First, we set new variables and put 1 in "refused". 
```{r}
recs=read.csv("recs.csv")

for (i in 1:9){
  recs[,60+i]=0
}

names(recs)[61:69]=c("refused","white","black or african american","asian","american indian or alaska native",
                     "native hawaiian or other pacific islander", "multiple respones selected", "others","hispanic")


recs[recs$HH_RACE==-7,61]=1

```


Next, we put 1 in each variable corresponding to "HH_RACE"
```{r}
for(i in 1:6){
  recs[recs$HH_RACE==i,61+i]=1
}
```

```{r}
recs[recs$HH_RACE==97,68]=1
```

For "Don't Know" in "HH_RACE", we put NA.
```{r}
recs[recs$HH_RACE==-8,c(61:69)]=NA
```


We set the hispanic variable. Notice that it is possible that both hispanic and white take 1 since hispanic is not a race but a cultural group of people.
```{r}
recs[recs$HH_HISP==-7,61]=1
recs[recs$HH_HISP==-8,c(61:69)]=NA
recs[recs$HH_HISP==1,69]=1
```