---
title: "Combined"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(MASS)
```

* Read csv file
```{r}
veh = read.csv("vehpub.csv")
hh = read.csv("hhpub.csv")
```

* Recode for HHFAMNIC
```{r}
AVGINCOME = hh$HHFAMINC
AVGINCOME[hh$HHFAMINC == '1'] = 10000
AVGINCOME[hh$HHFAMINC == '2'] = (10000+14999)/2
AVGINCOME[hh$HHFAMINC == '3'] = (15000+24999)/2
AVGINCOME[hh$HHFAMINC == '4'] = (25000+34999)/2
AVGINCOME[hh$HHFAMINC == '5'] = (35000+49999)/2
AVGINCOME[hh$HHFAMINC == '6'] = (50000+74999)/2
AVGINCOME[hh$HHFAMINC == '7'] = (75000+99999)/2
AVGINCOME[hh$HHFAMINC == '8'] = (100000+124999)/2
AVGINCOME[hh$HHFAMINC == '9'] = (125000+149999)/2
AVGINCOME[hh$HHFAMINC == '10'] = (150000+199999)/2#
AVGINCOME[hh$HHFAMINC == '11'] = 200000
AVGINCOME[hh$HHFAMINC < 0] = NA
hh$HHFAMINC = AVGINCOME
```

* Aggregate bestmile 
```{r}
bestmile = data.frame("HOUSEID" = veh$HOUSEID, "BESTMILE" = veh$BESTMILE)
bestmile = aggregate(bestmile$BESTMILE, by=list(bestmile$HOUSEID), FUN=sum)
names(bestmile) = c("HOUSEID", "BESTMILE")
recs = data.frame(merge(hh, bestmile, by = "HOUSEID"))
```

* National Household Travel Survey

We will created new dummy variables for races. When we use a regression model, we have to choose the baseline dummy to prevent "Multicollinearity". 

Supporting info: https://analyticstraining.com/understanding-dummy-variable-traps-regression/


First, we set new variables and put 1 in "refused". 
```{r}
for (i in 0:8){
  recs[, 60+i] = 0
}

names(recs)[60:68]=c("refused","white","black or african american","asian","american indian or alaska native",
                     "native hawaiian or other pacific islander", "multiple respones selected", "others","hispanic")


recs[recs$HH_RACE==-7,60]=1

```


Next, we put 1 in each variable corresponding to "HH_RACE"
```{r}
for(i in 1:6){
  recs[recs$HH_RACE==i,60+i]=1
}
```

```{r}
recs[recs$HH_RACE==97,67]=1
```

For "Don't Know" in "HH_RACE", we put NA.
```{r}
recs[recs$HH_RACE==-8,c(60:68)]=NA
```


We set the hispanic variable. Notice that it is possible that both hispanic and white take 1 since hispanic is not a race but a cultural group of people.
```{r}
recs[recs$HH_HISP==-7,60]=1
recs[recs$HH_HISP==-8,c(60:68)]=NA
recs[recs$HH_HISP==1,68]=1
```


* selecting variables appeared in census data
```{r}
dat <- data.frame(recs$DRVRCNT, recs$CNTTDHH, recs$HHFAMINC, recs$HHSIZE, recs$HHVEHCNT, recs$white, recs$BESTMILE)
colnames(dat) = c("DRVRCNT", "CNTTDHH", "HHFAMINC", "HHSIZE", "HHVEHCNT", "white", "bestmile")
```


```{r}
state.null <- lm(bestmile ~ 1, data = dat)
state.full <- lm(bestmile ~ DRVRCNT + CNTTDHH + HHFAMINC + HHSIZE + HHVEHCNT + white, data=dat)
state.step <- stepAIC(state.null, scope = formula(state.full),  direction = "forward", na.omit = TRUE)
summary(state.step)
```

